---
title: "Homework6"
author: "Jialiang Hua"
date: "12/2/2021"
output: github_document
---


```{r setup, include = FALSE}
library(tidyverse)
library(p8105.datasets)
library(modelr)
library(mgcv)
library(rvest)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

# Problem 1

## Import the data
```{r }
# Check for missing data
anyNA(read_csv("./data/birthweight.csv"))

birthweight_df = 
  read_csv("./data/birthweight.csv") %>% 
  mutate(
    babysex = case_when(
      babysex == 1 ~ "Male",
      babysex == 2 ~ "Female"
    ),
    frace = case_when(
      frace == 1 ~ "White",
      frace == 2 ~ "Black",
      frace == 3 ~ "Asian",
      frace == 4 ~ "Puerto Rican",
      frace == 8 ~ "Other",
      frace == 9 ~ "Unknown"
    ),
    malform = case_when(
      malform == 0 ~ "absent", 
      malform == 1 ~ "present"
    ),
    mrace = case_when(
      mrace == 1 ~ "White", 
      mrace == 2 ~ "Black", 
      mrace == 3 ~ "Asian", 
      frace == 4 ~ "Puerto Rican",
      frace == 8 ~ "Other"
    )
  ) %>% 
  mutate(
    babysex = as.factor(babysex),
    frace = as.factor(frace),
    malform = as.factor(malform),
    mrace = as.factor(mrace)
  ) 
```

## Set two models 
```{r}
model1 = lm(bwt ~ blength + gaweeks, data = birthweight_df)
broom::tidy(model1)
model2 = lm(bwt ~ bhead + blength + babysex + bhead*blength + blength*babysex + bhead*babysex + bhead*blength*babysex, data = birthweight_df)
broom::tidy(model2)
```

## Propose a model

**1. Predictor Selection - We use backward to build the model**

We fit a regression using all predictors, and use AIC criterion for var selection, from which we choose the model with the smallest value.

```{r }
all_fit = lm(bwt ~ babysex + bhead + blength + fincome + frace + gaweeks + malform + menarche + mheight + momage + mrace + parity + pnumlbw + pnumsga + ppbmi + ppwt + smoken + wtgain,data = birthweight_df)
broom::tidy(all_fit) 
step(all_fit, direction = 'backward') %>% broom::tidy()
```

**2. Get the final model**

According to the result of first step, we can get some reasonable predictors which we can use to build the model.

```{r }
best_model = lm(bwt ~ fincome + frace + parity + mrace + babysex + mheight+ ppwt+ gaweeks + smoken + wtgain + blength + bhead, data = birthweight_df)
broom::tidy(best_model)
```

**3. Make a plot of the "best" model**

```{r }
# a plot of model residuals against fitted values
birthweight_df %>% 
  add_residuals(best_model) %>% 
  add_predictions(best_model) %>% 
  ggplot(aes( x = pred, y = resid)) +
  geom_point(alpha = 0.3)

```

Everything is centered around 0, and it makes sense, and most points are scatter around roughly prediction = 3200, but there are some departure towards left in prediction and some towards up in residuals, which means that if baby birth weight tends low, the residuals will become high.


## Compare these models

**1. Cross Validation**
```{r }
cv_df = 
  crossv_mc(birthweight_df, 100)
cv_df = 
  cv_df %>% 
  mutate(
    firmod = map(.x = train, ~lm(bwt ~ blength + gaweeks, data = birthweight_df)),
    secmod = map(.x = train, ~lm(bwt ~ bhead + blength + babysex + bhead*blength + blength*babysex + bhead*babysex + bhead*blength*babysex, data = birthweight_df)),
    bestmod = map(.x = train, ~lm(bwt ~ fincome + frace + parity + mrace + babysex + mheight+ ppwt+ gaweeks + smoken + wtgain + blength + bhead, data = birthweight_df))
  ) %>% 
  mutate(
    rmse_model1 = map2_dbl(.x = firmod, .y = test, ~rmse(model = .x, data =.y)),
    rmse_model2 = map2_dbl(.x = secmod, .y = test, ~rmse(model = .x, data =.y)),
    rmse_bestmodel = map2_dbl(.x = bestmod, .y = test, ~rmse(model = .x, data =.y))
  )
```


**2. See the distribution of three models RMSE**
```{r }
cv_df %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "model",
    values_to = "rmse",
    names_prefix = "rmse_"
  ) %>% 
  ggplot(aes(x = model, y = rmse, color = model)) +
  geom_violin() +
  stat_summary(fun = "median", color = "blue") +
  labs(
    x = "Model",
    y = "RMSE",
    title = "RMSEs of Different Models"
  )
```

From the plot, we can see that among three models, the model 1 has the lowest RMSE, which indicates that it is a better model than the other two models.


