---
title: "Homework6"
author: "Jialiang Hua"
date: "12/2/2021"
output: github_document
---


```{r setup, include = FALSE}
library(tidyverse)
library(p8105.datasets)
library(modelr)
library(mgcv)
library(rvest)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

# Problem 1

## Import the data
```{r }
# Check for missing data
anyNA(read_csv("./data/birthweight.csv"))

birthweight_df = 
  read_csv("./data/birthweight.csv") %>% 
  mutate(
    babysex = case_when(
      babysex == 1 ~ "Male",
      babysex == 2 ~ "Female"
    ),
    frace = case_when(
      frace == 1 ~ "White",
      frace == 2 ~ "Black",
      frace == 3 ~ "Asian",
      frace == 4 ~ "Puerto Rican",
      frace == 8 ~ "Other",
      frace == 9 ~ "Unknown"
    ),
    malform = case_when(
      malform == 0 ~ "absent", 
      malform == 1 ~ "present"
    ),
    mrace = case_when(
      mrace == 1 ~ "White", 
      mrace == 2 ~ "Black", 
      mrace == 3 ~ "Asian", 
      frace == 4 ~ "Puerto Rican",
      frace == 8 ~ "Other"
    )
  ) %>% 
  mutate(
    babysex = as.factor(babysex),
    frace = as.factor(frace),
    malform = as.factor(malform),
    mrace = as.factor(mrace)
  ) 
```

## Set two models 
```{r}
model1 = lm(bwt ~ blength + gaweeks, data = birthweight_df)
broom::tidy(model1)
model2 = lm(bwt ~ bhead + blength + babysex + bhead*blength + blength*babysex + bhead*babysex + bhead*blength*babysex, data = birthweight_df)
broom::tidy(model2)
```

## Propose a model

**1. Predictor Selection - We use backward to build the model**

We fit a regression using all predictors, and use AIC criterion for var selection, from which we choose the model with the smallest value.

```{r }
all_fit = lm(bwt ~ babysex + bhead + blength + fincome + frace + gaweeks + malform + menarche + mheight + momage + mrace + parity + pnumlbw + pnumsga + ppbmi + ppwt + smoken + wtgain,data = birthweight_df)
broom::tidy(all_fit) 
step(all_fit, direction = 'backward') %>% broom::tidy()
```

**2. Get the final model**

According to the result of first step, we can get some reasonable predictors which we can use to build the model.

```{r }
best_model = lm(bwt ~ fincome + frace + parity + mrace + babysex + mheight+ ppwt+ gaweeks + smoken + wtgain + blength + bhead, data = birthweight_df)
broom::tidy(best_model)
```

**3. Make a plot of the "best" model**

```{r }
# a plot of model residuals against fitted values
birthweight_df %>% 
  add_residuals(best_model) %>% 
  add_predictions(best_model) %>% 
  ggplot(aes( x = pred, y = resid)) +
  geom_point(alpha = 0.3)

```

Everything is centered around 0, and it makes sense, and most points are scatter around roughly prediction = 3200, but there are some departure towards left in prediction and some towards up in residuals, which means that if baby birth weight tends low, the residuals will become high.


## Compare these models

**1. Cross Validation**
```{r }
cv_df = 
  crossv_mc(birthweight_df, 100)
cv_df = 
  cv_df %>% 
  mutate(
    firmod = map(.x = train, ~lm(bwt ~ blength + gaweeks, data = birthweight_df)),
    secmod = map(.x = train, ~lm(bwt ~ bhead + blength + babysex + bhead*blength + blength*babysex + bhead*babysex + bhead*blength*babysex, data = birthweight_df)),
    bestmod = map(.x = train, ~lm(bwt ~ fincome + frace + parity + mrace + babysex + mheight+ ppwt+ gaweeks + smoken + wtgain + blength + bhead, data = birthweight_df))
  ) %>% 
  mutate(
    rmse_model1 = map2_dbl(.x = firmod, .y = test, ~rmse(model = .x, data =.y)),
    rmse_model2 = map2_dbl(.x = secmod, .y = test, ~rmse(model = .x, data =.y)),
    rmse_bestmodel = map2_dbl(.x = bestmod, .y = test, ~rmse(model = .x, data =.y))
  )
```


**2. See the distribution of three models RMSE**
```{r }
cv_df %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "model",
    values_to = "rmse",
    names_prefix = "rmse_"
  ) %>% 
  ggplot(aes(x = model, y = rmse, color = model)) +
  geom_violin() +
  stat_summary(fun = "median", color = "blue") +
  labs(
    x = "Model",
    y = "RMSE",
    title = "RMSEs of Different Models"
  )
```

From the plot, we can see that among three models, the model 1 has the lowest RMSE, which indicates that it is a better model than the other two models.


## Problem 2

```{r import_data}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```

let's bootstrap

```{r bootstrap}
weather_boot =
  weather_df %>% 
  drop_na() %>% 
  bootstrap(5000, id = "strap_number") %>% 
  mutate(
    models = map(.x = strap, ~lm(tmax ~ tmin, data = .x)),
    results = map(models, broom::tidy),
    result_r = map(models, broom::glance)
  ) %>% 
  select(strap_number, results, result_r) %>% 
  unnest(results, result_r)
```

Calculate $log(\beta_{0} * \beta_{1})$

```{r callog}
callog =
  weather_boot %>% 
  dplyr::select(strap_number, term, estimate) %>% 
  pivot_wider(names_from = term,
              values_from = estimate) %>% 
  rename(intercept ="(Intercept)") %>% 
  mutate(logBB = log10(intercept*tmin))
```

Plot the distribution of $log(\beta_{0} * \beta_{1})$

```{r densi_BB}
callog %>% 
  ggplot(aes(x = logBB)) +
  geom_density() + 
  xlab("log(B0 * B1)") +
  ggtitle("Distribution of log(B0 * B1)")
```

It could find from the figure that the distribution of $log(\beta_{0} * \beta_{1})$ is approximately normal, when $log(\beta_{0} * \beta_{1})$ around 0.875, it has maximum density. The distribution is little right-skewed, which may be better with higher bootstrap times.


Calculate the 95% CI

```{r CI_BB}
callog %>% 
  summarize(
    ci_lower = quantile(logBB, 0.025),
    ci_upper = quantile(logBB, 0.975)
  ) %>% 
  knitr::kable()
```

Calculate $r^2$

```{r r_square}
r_square =
  weather_boot %>% 
  filter(term == "tmin") %>% 
  dplyr::select(r.squared) 
```

Plot the distribution of  $r^2$

```{r densi_r}
r_square %>% 
  ggplot(aes(x = r.squared)) +
  geom_density() + 
  xlab("r square") +
  ggtitle("Distribution of r square")
```

From the figure, we could find that the distribution of  $r^2$ is approximately normal, when  $r^2$ around 0.91, it has maximum density. $r^2$ indicates the percentage of the response variable variation that is explained by a linear model. When $r^2$ is closer to 1, it means model fit data better. From the distribution, it seems the model shows good fitness to the data.


Calculate the 95% CI

```{r CI_r}
r_square %>% 
  summarize(
    ci_lower = quantile(r.squared, 0.025),
    ci_upper = quantile(r.squared,0.975)
  ) %>% 
  knitr::kable()
```